The Chemistry Development Kit (CDK) v2.0: atom typing, depiction, molecular formulas, and substructure searching

### 2017-03-26 article.tex
Added a section on user fora

>>>>

\subsubsection*{Support}

Besides the aforementioned sources of documentation, the project has additional
sources of support. First, the issue tracker welcomes questions and other types
of support requests, available at \url{https://github.com/cdk/cdk/issues}.
The mailing list is another place where support can be requested, while the
archives document many past user questions. The list and archives can be
accessed from \url{https://sourceforge.net/p/cdk/mailman/cdk-user/}.
